Multi-objective autotuning of MobileNets\\ across the full software/hardware stack

### 2018-05-31 dissemination.publication/08da9685582866a0/paper.tex
clean up

%Conference
\acmConference[ReQuEST at ASPLOS'18]{1st ACM SIGARCH Reproducible Quality-Efficient Systems Tournament to Co-design Pareto-efficient Deep Learning}{March 2018}{Williamsburg, VA, USA}
\acmYear{2018}
\copyrightyear{2018}

>>>>

%Conference
\acmConference[ReQuEST at ASPLOS'18]{1st ACM Reproducible Quality-Efficient Systems Tournament on Co-designing Pareto-efficient Deep Learning}{March 2018}{Williamsburg, VA, USA}
\acmYear{2018}
\copyrightyear{2018}
